ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Clarify the purpose of the YAML section
Respond to #5

This section provides a brief introduction to the current version of the
\ck{} database format, v0.1.6, which represents a functional standard
for documenting autoignition measurements in shock tubes and rapid compression machines.
Here we do not include a complete listing of available fields; a complete reference for the
schema can be found in the online
documentation.\footnote{\url{https://pr-omethe-us.github.io/PyKED/schema-docs.html}}
In Section~\ref{sec:usage-example}, we provide examples of \ck{} files and
representative use cases. We indicate \yabox|yaml| keywords or values using text with
gray background, and \pybox|Python| code using text with a yellow background.

>>>>

This section provides an introduction to the current version of the \ck{} database format, v0.1.6,
which represents a functional standard for documenting autoignition measurements in shock tubes and
rapid compression machines. Here we describe the fields that a user creating a \ck{} file is likely
to use. There are several fields that are used internally in the schema that are not described here,
but can be found in the online documentation for the
schema.\footnote{\url{https://pr-omethe-us.github.io/PyKED/schema-docs.html}} In
Section~\ref{sec:usage-example}, we provide examples of \ck{} files and representative use cases. We
indicate \yabox|yaml| keywords or values using text with gray background, and \pybox|Python| code
using text with a yellow background.
